RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
changed in an attempt to draw the distinction between community conventions for flat text, and standards that have been described in technical recommendations under the auspices of the W3C (i.e. "web standards")

For example, the currently popular NEXUS file format cannot consistently
represent horizontal gene transfer or ambiguity in reading a character
(such as a DNA sequence base pair).  This has led developers to
repeatedly add small modifications to the standard to meet the needs
of their own software, which results in mutually incompatible dialects
that largely defeat the advantages of a shared standard file format.
NeXML was developed to addresses each of these problems `r citep("Vos NeXML Systematic Biology")`  
by drawing on state-of-the-art data management technology.

>>>>

For example, the currently popular NEXUS file format cannot consistently
represent horizontal gene transfer or ambiguity in reading a character
(such as a DNA sequence base pair).  This has led developers to
repeatedly add small modifications to the standard to meet the needs
of their own software, which results in mutually incompatible dialects
that largely defeat the advantages of a shared  file format.
NeXML was developed to addresses each of these problems `r citep("Vos NeXML Systematic Biology")`  
by drawing on robust web standards in data representation.
